Robot Team II: Electric Boogaloo

### 2023-11-27 paper/paper.tex
updated paper with abstract notes

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Fill this out last}

>>>>

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{A robust characterization of model uncertainties is critical for any time-sensitive or dangerous application...To that end we employ a combination of model stacking together with Conformal Prediction by which we are able to blend together a variety of ML models while simultaneously estimating confidence intervals for the resulting predictions. }
